The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
Updated introduction

%3Purpose
Modifications to deployed APIs may negatively impact its users. It is therefore important to investigate why these changes occur. Understanding the motives behind the changes could help API designers to  prevent potential future changes to their APIs. Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.

%4Gap in Literature
Studies that explore the intent behind API modifications exist \cite{hou2011exploring}. The area of programming language APIs is well-explored \cite{hou2011exploring, shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}. To the best of our knowledge, no studies that explore API evolution have until now been performed on embedded platform APIs.

%5Purpose of the study
The goal of the study was twofold. Firstly, the aim was to explore what the driving forces behind API evolution are, and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes. With this information, we could determine to what extent these change decisions can be reverse engineered. 
%6Why this is important for the case company.
This study has many potential benefits for the case company. Identifying the types of changes that occur when an API evolves will improve communication and discussions regarding maintenance and evolution tasks. This improved communication could provide a common language that developers, users and management can use to discuss potential evolution of the APIs. Understanding the evolution theories could further assist understanding of how change will occur and how to plan for it. Lastly, by keeping a history of changes to an API over time, trends can be identified which could help with future API design.

%I would suggest that paragraph #6 is merged with paragraph 3. (I.e. move #6 in between #3 and #4). Otherwise we have a purpose in two places and the most important part of the purpose in the end of the intro, which isn't good.

%The first sentence of paragraph 6 is very subjective and doesn't really add much

%I also think the gap (#4) has to be re-written. Right now it doesn't say much at all. And the 2nd sentence makes no sense at all (2refs="well-explored" and 1ref="few")

%Otherwise really good... like the #6 a lot

>>>>

%3Purpose
Modifications to deployed APIs may negatively impact its users. It is therefore important to investigate why these changes occur. Understanding the motives behind the changes could help API designers to  prevent potential future changes to their APIs. Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives. 
%3 cont.d - Why this is important for the case company.

Identifying the types of changes that occur when an API evolves will improve communication and discussions regarding maintenance and evolution tasks for the case company. This improved communication could provide a common language that developers, users and management can use to discuss potential evolution of the APIs. Understanding the evolution theories could further assist understanding of how change will occur and how to plan for it. Lastly, by keeping a history of changes to an API over time, trends can be identified which could help with future API design.

%4Gap in Literature
Previous studies have investigated programming language APIs, libraries or frameworks focusing on causes and affects of modifications to APIs \cite{hou2011exploring, shi2011empirical, dig2005role}. However, to the best of our knowledge, no studies have been performed on embedded platform APIs from a software evolution perspective.

%Goal of the study
The goal of the study was twofold. Firstly, the aim was to explore what are the driving forces behind API evolution and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes. With this information, we could determine to what extent these change decisions can be reverse engineered.
